Corrplot

### 2022-03-17 analysis/corrplot.Rmd
Revert "fix: working directory for targets"
This reverts commit cac14f630848b078c39aee7344862d418fcdcb52.
feat: list correlations in table

```{r corrplot_setup, message = FALSE}
library("corrplot")
library("targets")

withr::with_dir(rprojroot::find_rstudio_root_file(), {
    tar_load(imp_data)
})
```

@@

@@

>>>>

```{r corrplot_setup, message = FALSE}
library("corrplot")
library("targets")
tar_load(imp_data)
```

@@

## Plot

@@

## Table

```{r cortbl}
ut <- upper.tri(cr)
nms <- paste(
    colnames(cr)[col(cr)[ut]],
    rownames(cr)[row(cr)[ut]],
    sep = ":"
)
tbl <- data.frame(Values = nms, Correlation = cr[ut])
tbl <- tbl[order(-abs(tbl$Correlation)),]
knitr::kable(tbl, header = TRUE, row.names = FALSE, digits = 3L)
```
